### 2023-05-08 Documentation/UFMG/PFCII/Apendices/ApendiceA.tex
documentation

\begin{figure}[H]
  \centering
  \resizebox{150mm}{!}{\includegraphics{Figuras/setup_pic.jpg}}
  \caption{EHDA automation system setup}
  \label{fig:setup_pic}
\end{figure}

@@

The current being measured by the Oscilloscope use its internal impedance. 
The \emph{TiePie} oscilloscope model has two impedance options, 1Mohm or 2Mohms. 
Selecting one or other can multiply or divide your current measurement by 2. 
By default, we are using the 2Mohm differential input, however it was noticed that using the 1Mohm resistance might reduce noise. 
A proposal is to configure the 1Mohm resistance in the \emph{configuration\_tiepie.py} file and evaluate its performance.

>>>>

\begin{figure}[H]
  \centering
  \resizebox{150mm}{!}{\includegraphics{Figuras/setup_pic.jpg}}
  \caption{EHDA automation system setup used for experiments.}
  \label{fig:setup_pic}
\end{figure}

@@

The current being measured by the Oscilloscope use its internal impedance. 
The \emph{TiePie} oscilloscope model has two impedance options, 1Mohm or 2Mohms. 
Selecting one or other will multiply or divide your current measurement by 2. 
By default, it is being used 2Mohm differential input, however it was noticed that using the 1Mohm resistance might reduce noise. 
A proposal is to configure the 1Mohm resistance in the \emph{configuration\_tiepie.py} file and evaluate its performance.

### 2023-05-08 Documentation/UFMG/PFCII/Conclusion/Conclusion.tex
documentation

To continue, my proposal would be to prioritize the improvement of the classification step. 
Ideally, we could use machine learning or another algorithm to ensure accurate classification with a broad range of liquids.
By achieving a reliable classification, we can then implement more effective controller logic or approaches. 
In this regard, I would like to present the concept of a fuzzy controller as a potential solution.

@@

    When it comes to classifying spraying modes, machine learning represents a sophisticated and trendy approach.
    This project was designed in order to substitute our statistical classifier for a more general and accurate algorithm.

@@

        One challenge in implementing the controller in this project is that we don't have a real value as feedback, instead, the feedback from the controller loop is a classification, which makes it difficult to apply many of the principles of control theory that are designed for continuous control. 
        As this project involves logical control, it requires a different approach.

@@

            \begin{figure}[H]
                \centering
                \includegraphics[width=17cm]{Figuras/fuzzy/Fuzzyy.png}
                \caption{fuzzyfication of input and defuzzyfication of output}
                \label{fig:fuzzyy}
            \end{figure}

        Our controller is an algorithm that calculate the output with a geometrical calculus on the membership functions of the input and output according to our rules listed below.

@@

    \begin{figure}[H]
        \centering
        \includegraphics[width=17cm]{Figuras/fuzzy/test3.png}
        \caption{fuzzyfication of input and defuzzyfication of output}
        \label{fig:fuzzyy1}
    \end{figure}

@@

        The current project builds on this foundation and highlights several key results, including the integration of a liquid pump into the software and the development of a routine that can be easily modeled to fit a control model, making it straightforward to implement new control algorithms or experiment routines. 
        The software was also remodeled to support threads, allowing for the separation of each subsystem and the exchange of data between them using queue data structures. A classification for multi-jet spraying mode was developed, along with a simple controller to demonstrate proof of concept. 
        Additionally, the saving of data was optimized to a real-time streaming format and expanded to include more sensor data. Finally, the algorithm usability was restructured to make it more intuitive for users through the use of a setup file.

>>>>

To continue, a proposal is to prioritize the improvement of the classification step. 
Ideally using machine learning or another algorithm to ensure accurate classification with a broad range of liquids.
By achieving a reliable classification, a more effective controller logic or approaches can be implemented. 
In this regard, a concept of a fuzzy controller will be presented as a potential solution.

@@

    When it comes to classifying spraying modes, machine learning represents a sophisticated and trendy approach.
    This project was designed in order to substitute the statistical classifier for a more general and accurate algorithm.

@@

        One challenge in implementing the controller in this project is that it does not have a real value as feedback, instead, the feedback from the controller loop is a classification, which makes it difficult to apply many of the principles of control theory that are designed for continuous control. 
        As this project involves logical control, it requires a different approach.

@@

            \begin{figure}[H]
                \centering
                \includegraphics[width=17cm]{Figuras/fuzzy/Fuzzyy.png}
                \caption{fuzzyfication of input and defuzzyfication of output.}
                \label{fig:fuzzyy}
            \end{figure}

        The controller is an algorithm that calculate the output with a geometrical calculus on the membership functions of the input and output according to the rules listed below.

@@

    \begin{figure}[H]
        \centering
        \includegraphics[width=17cm]{Figuras/fuzzy/test3.png}
        \caption{Test implemented to validate the concept of fuzzy controller in this project.}
        \label{fig:fuzzyy1}
    \end{figure}

@@

        The current project builds on this foundation and highlights several key results, including the integration of a liquid pump into the software and the development of a routine that can be easily modeled to fit a control model, making it straightforward to implement new control algorithms or experiment routines.

        The software was also remodeled to support threads, allowing for the separation of each subsystem and the exchange of data between them using queue data structures. A classification for multi-jet spraying mode was developed, along with a simple controller to demonstrate proof of concept. 
        Additionally, the saving of data was optimized to a real-time streaming format and expanded to include more sensor data. Finally, the algorithm usability was restructured to make it more intuitive for users through the use of a setup file.

### 2023-05-08 Documentation/UFMG/PFCII/Introduction/Introduction.tex
documentation

EHDA research has contributed as an important tool for the development of technology. 
The advantage of using electrospray is precision and uniform size and shape of droplets creation. 
Specially in certain spraying modes.

Although there are applications of EHDA in industry, the stabilization of the conical jet spray mode is mostly done empirically and based on average current measurements.

@@

This project aims to give continuity to the previous student work\cite{Monica}, 
Mônica, who focused in detecting undesired discharges (sparks) in the system accusing high electric potential. 
For that, she developed a python software routine to connect most of the peripherals and analyzed the current data.
Her work corroborates the validation of this project motivating its continuation on development and optimization.

@@

% Faça uma breve apresentação da empresa ou laboratório onde o projeto é desenvolvido. Fale um pouco da história da empresa, do mercado em que atua, da sua organização, do departamento em que está inserido o projeto, etc. Descreva também o seu vínculo com a empresa.

@@

Chapter \ref{chap:system_description} describes the system that was implemented to make this project work, along with the instruments and models used to apply our methodology.

Chapter \ref{chap:Methodology} presents the methodology applied in our experiments to validate our system.

In Chapter \ref{chap:Results}, we present our results and engage in discussions comparing the knowledge acquired through literature review.

Finally, in Chapter \ref{chap:conclusion}, we conclude our document with discussions about the goals achieved and areas for potential optimization.

>>>>

EHDA research has contributed as an important tool for the development of technology. 
The advantage of using electrospray is precision and uniform size and shape of droplets creation, specially in certain spraying modes. 
Although there are many applications of EHDA in industry, the stabilization of the conical jet spray mode is mostly done empirically and based on average current measurements.

@@

This project aims to give continuity to the previous student work\cite{Monica}, who focused in detecting undesired discharges (sparks) in the system accusing high electric potential. 
For that, it was developed a python software routine to connect most of the peripherals and analyzed the current data.
Her work corroborates the validation of this project motivating its continuation on development and optimization.

@@

@@

Chapter \ref{chap:system_description} describes the system that was implemented to make this project work, along with the instruments and models used to apply the methodology.

Chapter \ref{chap:Methodology} presents the methodology applied in experiments to validate the system.

In Chapter \ref{chap:Results}, it is presented results and engage in discussions comparing the knowledge acquired through literature review.

Finally, in Chapter \ref{chap:conclusion}, this document is concluded with discussions about the goals achieved and areas for potential optimization.

### 2023-05-08 Documentation/UFMG/PFCII/LiteratureReview/LiteratureReview.tex
documentation

The electrospraying of liquids herein is referred to as electrohydrodynamic atomization (EHDA). The atomization by primarily electrical (electro) forces of a liquid (hydro) that is moving (dynamic) during the atomization captures the essence of the phenomena.\cite{Grace}
That motion applies to the liquid certain velocity that is not enough to create the spray alone. Therefore, the electric field itself is the responsible for the spraying dynamics.\cite{prunet}
A stable balance between the capillary and field forces on the liquid suggest a \emph{quasi static} dynamics.
The feeding liquid is pulled through a small orifice by means of the applied voltage.
The droplets are accelerated towards the grounded electrode by the electric field.
The resulting spray is electrically charged, and the droplets repel one another.
For this reason, with a controlled environment we can reach a certain stable spraying mode as can be seen in the Figure \ref{fig:ehda_setup_ex2}.

@@

From the inception of EHDA until the present day, research has been carried out through manual means, involving the use of visual classification to determine the spraying mode either through cameras or by direct observation. It is advisable to employ a high-speed camera (HS) to accurately capture the spraying process as certain intermittent or dripping states may occur at a high frequency and be erroneously perceived as a stable condition.
The setup in figure \ref{fig:ehda_setup} shows the most common setup used for EHDA researchers.

@@

Therefore, many researches were made about the classification of the spraying mode measuring the current flowing through the nozzle to plate\cite{Sjaaks}\cite{Chen_Pui}. 
Evaluating the current data can give us valuable information about the spraying behavior.
Figure \ref{fig:microdripping_current_pic} illustrate a sample of current measured in our system during a dripping of a charged liquid. 
We can visually identify the signal of two droplets generated in this time frame.

@@

The electric spray current is a critical variable that has been extensively researched by multiple authors\cite{prunet}\cite{Chen_Pui}\cite{gananCalvo}, resulting in scaling laws that express the relationship between liquid flow rate, conductivity, surface tension, density, and droplet diameter. 
These scaling laws can predict the size and charge of emitted droplets, making them useful tools for electrospraying practitioners. 
Obtaining scaling laws is necessary for characterizing an electrospraying system and gaining a better understanding of the process mechanisms. 
In equation \ref{eq:i_chenpui} we have the current flowing through the charged liquid during a Taylor\cite{taylor} cone jet.

@@

Since 1915 with his pioneering work in EHDA, Zeleny\cite{zeleny14} observed several functioning modes with very different characteristics.
Years later the same phenomena was noticed by other scientists, but the classification of these modes were still not well-defined by the community.
For that Cloupeau and Prunet-Foch\cite{prunet} proposed spray mode classifications based in what they have seen experimentally, and it's still being used as basis for EHDA researches.

Figure \ref{fig:spraying_modes} shows 3 spraying dynamics that we are most interesting in this project.

@@

Through the various classifications and subclassifications of spraying defined in literature we are going to aggregate some of them and separate between 5 modes as reffered below in order of growing electric potential:

@@

Dripping mode happens when the electric field applied is not enough to change the meniscus shape, phenomena called field enhanced dripping.
In that situation the liquid droplet has, in general, size bigger than the capillary and low frequency intervals between each drop.

@@

Intermittent mode is defined when the electric field forces start to have a considerable effect in the meniscus and droplet formation. 
This mode can be identified by its pulsating manner.
In this mode the droplet size is smaller than the nozzle, phenomena called microdripping, and the dripping frequency increases with the increasing of the field applied.
Figure \ref{fig:intermittent_example} illustrates 3 different dynamics herein considered as intermittent.

@@

In Taylor cone, here referred as Cone Jet, the direction of the cone apex also varies depending on the balance of forces. 
With a fixed flow of liquid it is noticeable that the pointing direction curves and the meniscus reduce volume as we increase the electric potential until the moment the jet breaks into two or more jets going to the next classification.

@@

Zeleny's (1915)\cite{zeleny} paper was the first reference to multi-jet phenomena. In his experiments was observed:
\emph{"for voltages well above that for which the steady conical surface changed into a blurred agitated one, the appearance became a number of fine points with their attendant dark streaks arranged along the circumference of the raised edge".}

In recent times, researchers have made significant advancements in understanding multi-jet technology and have identified various profiles with distinct characteristics. Because of that, some authors can divide what we call multi jet in more classifications.
The multi jet mode is considered in this work when two or more spraying jets can be visualized in the HS camera and the current shows a stable profile.

@@

At even higher electric potentials, above of multi jet, the insulation between the electrodes start to breakdown, and we achieve a phenomenon of discharge.
Those can be easily classified because of its high current value.

This mode is also divided by other classes such as streamer corona or transient sparks discharges, but it's not in the scope of this work. 
Mônicas\cite{Monica} work was focused on how to predict that mode with the current analysis for safety in industrial applications.

@@

In this chapter we exhibit some electrospray theory that was important for the development of this project. 
Firstly, with a brief review about the physical concept behind the experiment. 
Then, I introduce how current analysis can be useful for our application citing works already done with this approach.
Finally, I end up the chapter defining what spraying modes classification will be considered and its properties.

>>>>

The electrospraying of liquids herein is referred to as electrohydrodynamic atomization (EHDA). The atomization by primarily electrical (electro) forces of a liquid (hydro) that is moving (dynamic) during the atomization captures the essence of the phenomenon.\cite{Grace}
That motion applies to the liquid certain velocity that is not enough to create the spray alone. Therefore, the electric field itself is the responsible for the spraying dynamics.\cite{prunet}
A stable balance between the capillary and field forces on the liquid suggest a \emph{quasi static} dynamics.
The feeding liquid is pulled through a small orifice by means of the applied voltage.
The droplets are accelerated towards the grounded electrode by the electric field.
The resulting spray is electrically charged, and the droplets repel one another.
For this reason, with a controlled environment a certain stable spraying mode can be reached as seen in the Figure \ref{fig:ehda_setup_ex2}.

@@

From the inception of EHDA until the present day, research has been carried out through manual means, involving the use of visual classification to determine the spraying mode either through cameras or by direct observation. It is advisable to employ a high-speed camera (HS) to accurately capture the spraying process as certain intermittent or dripping states may occur at a high frequency and be erroneously perceived as a stable condition.
The setup in Figure \ref{fig:ehda_setup} shows the most common setup used for EHDA researchers.

@@

Therefore, many researches were made about the classification of the spraying mode measuring the current flowing through the nozzle to plate\cite{Sjaaks}\cite{Chen_Pui}. 
Evaluating the current data gives valuable information about the spraying behavior.
Figure \ref{fig:microdripping_current_pic} illustrate a sample of current measured in the system during a dripping of a charged liquid. 
It can be visually identified the signal of two droplets generated in this time frame.

@@

The electric spray current is a critical variable that has been extensively researched by multiple authors\cite{prunet}\cite{Chen_Pui}\cite{gananCalvo}, resulting in scaling laws that express the relationship between liquid flow rate, conductivity, surface tension, density, and droplet diameter. 
These scaling laws can predict the size and charge of emitted droplets, making them useful tools for electrospraying practitioners. 
Obtaining scaling laws is necessary for characterizing an electrospraying system and gaining a better understanding of the process mechanisms. 
Equation \ref{eq:i_chenpui} calculates the current flowing through the charged liquid during a Taylor\cite{taylor} cone jet.

@@

Since 1915 with his pioneering work in EHDA, Zeleny\cite{zeleny14} observed several functioning modes with very different characteristics.
Years later the same circumstance was noticed by other scientists, but the classification of these modes were still not well-defined by the community.
For that Cloupeau and Prunet-Foch\cite{prunet} proposed spray mode classifications based on what they have seen experimentally, and it is still being used as basis for EHDA researches.

Figure \ref{fig:spraying_modes} shows 3 spraying dynamics that are most interesting in this project.

@@

Through the various classifications and subclassifications of spraying defined in literature it will be aggregated some of them and separated between 5 modes as explained below in order of growing electric potential.

@@

Dripping mode happens when the electric field applied is not enough to change the meniscus shape, phenomenon called field enhanced dripping.
In that situation the liquid droplet has, in general, size bigger than the capillary and low frequency intervals between each drop.

@@

Intermittent mode is defined when the electric field forces start to have a considerable effect in the meniscus and droplet formation. 
This mode can be identified by its pulsating manner.
In this mode the droplet size is smaller than the nozzle, situation called electric microdripping, and the dripping frequency increases with the increasing of the field applied.
Figure \ref{fig:intermittent_example} illustrates 3 different dynamics herein considered as intermittent.

@@

In Taylor cone, here referred as Cone Jet, the direction of the cone apex also varies depending on the balance of forces. 
With a fixed flow of liquid it is noticeable that the pointing direction curves and the meniscus reduce volume when increase the electric potential until the moment the jet breaks into two or more jets going to the next classification.

@@

Zeleny's (1915)\cite{zeleny} paper was the first reference to multi-jet mode. In his experiments was observed:
\emph{"for voltages well above that for which the steady conical surface changed into a blurred agitated one, the appearance became a number of fine points with their attendant dark streaks arranged along the circumference of the raised edge".}

In recent times, researchers have made significant advancements in understanding multi-jet technology and have identified various profiles with distinct characteristics. Because of that, some authors can divide what it is called multi jet in more classifications.
The multi jet mode is considered in this work when two or more spraying jets can be visualized in the HS camera and the current shows a stable profile.

@@

At even higher electric potentials, above of multi jet, the insulation between the electrodes start to breakdown, achieving an event of discharge, referred in this work as corona.
Those can be easily classified because of its high current value.

This mode is also divided by other classes such as streamer corona or transient sparks discharges, but it's not in the scope of this work. 
The previous student work was focused on how to predict that mode with the current analysis for safety in industrial applications.

@@

In this chapter it was exhibited some electrospray theory that was important for the development of this project. 
Firstly, with a brief review about the physical concept behind the experiment. 
Then, introduced how current analysis can be useful for applications citing works already done with this approach.
Finally, ending up the chapter defining what spraying modes classification will be considered and its properties.

### 2023-05-08 Documentation/UFMG/PFCII/Methodology/Methodology.tex
documentation

The classification is a key step in our routine and for being able to be used in multipurpose applications our classification must be able to run in real-time, which means it must be fast and automatic.
The goal is to improve and apply approaches of non-visual spraying classification using the current data collected from the system.

\subsection{Statistical Analysis}
In Sjaaks\cite{Sjaaks} work, the author exposed signal characteristics that can be used to classify the actual spraying mode with a sample of measured current using both time and frequency domain analysis.
We acquire the current data frame of 0.5s with 100 kHz as sampling frequency, with each current sample as 50 thousand current values. Through statistical analysis in these values such as mean and standard deviation we apply in our automatic classification the relative standard deviation. Which is referred as the sample standard deviation divided by the sample mean values. 
Figure \ref{fig:sjaaks_statistical_class} illustrate data samples being classified using Sjaaks method.

@@

To classify the multi jet, after running many steps experiments I noticed that the multi jet signal has a similar shape as the cone jet but with a step in its current mean, also the cone jet current was almost fixed in all its voltage range. 
These effects were exposed by Ryan\cite{Ryan}. In his work he defines the relation between current per jet in both cone jet and multi jet modes.

With that, I implemented the classification of the multi jet when the current mean is 1.14 above the expected cone jet current mean. 
The cone jet current can be calculated by the scaling laws \ref{sec:scalling-laws} formula.
The factor value of 1.14 was found by repeating a lot of experiments with the same liquid (pure ethanol), but varying the flow rate and the voltage. This factor value is just applied for pure ethanol, the liquid used in all experiments in this work.
The classification in the algorithm was divided in three steps as shown below.

@@

    The program developed is capable of running different types of routines and with an easy way to implement new strategies.
    Continuing the methodology, in the setup json file there is a "sequence" attribute which can be chosen between "ramp", "step", "map" or "control".
    The controller thread will manage what the algorithm must do for each sequence.
    Following our control model\ref{fig:control_model_fig}, the controller outputs (voltage and flow rate) are the actuators signal.
    The sampling rate is fixed to 0.5 seconds for all the experiments, and it's managed by the data\_acquisiton\_thread\ref{subsec:data_aquisition}.

@@

    In Figure \ref{fig:map2Data_fig} we can see the data acquired in this mapping experiments. The liquid used is pure ethanol. 
    Note that the experiment is composed of loops that increase voltage, change flow rate and repeat.

    \begin{figure}[H]
        \center
        \includegraphics[width=15cm]{Figuras/report2/map2Data.png}
        \caption{Mapping Experiment data collected. The figure has 3 graphs with shared x-axis representing the samples collected. The first is the current values collected through all the experiment.
        The second is the voltage values applied in each window of data collected. The colors represent the spraying classification defined by our routine.
        The third graph shows the current mean value of each data sample.}
        \label{fig:map2Data_fig}
    \end{figure}

    With all the data collected, classified and saved in real time, we can do further analysis and studies. For example, Figure \ref{fig:map3Data_fig} illustrate the data classified by our algorithm and displayed in a Voltage X Flow rate range of spraying modes with a specific liquid setup so that we can compare the automatic results with previous researches, such as showed in figure \ref{fig:ganan_calvo_fig} and validate the algorithm.

    \begin{figure}[H]
        \center
        \includegraphics[width=15cm]{Figuras/report4/map-2023-03-02.png}
        \caption{Mapping Experiment for pure ethanol in ambient conditions with our capillary setup. The map shows the stability region of each electrospraying mode in the voltage and flow rate range.}
        \label{fig:map3Data_fig}
    \end{figure}

@@

    The control sequence is the only from our list of sequences that actually uses the feedback classification value. 
    As it is a closed loop control, the controller must be able to stabilize the system in the desired conditions.
    A simple controller algorithm is represented in algorithm \ref{alg:simple_controller}, and it was used as a proof of concept.
    Its results can be seen in results section \ref{sec:controller_results}.

@@

This chapter \ref{chap:Methodology} exhibits how the knowledge from chapter \ref{chap:lit_review} was implemented with a control and automation engineering approach in order to achieve our goals. 
Next chapter \ref{chap:Results}, we will discuss the results reached.

>>>>

The classification is a key step in this routine and for being able to be used in multipurpose applications the classification must be able to run in real-time, which means it must be fast and automatic.
The goal is to improve and apply approaches of non-visual spraying classification using the current data collected from the system.

\subsection{Statistical Analysis}
In Sjaaks\cite{Sjaaks} work, the author exposed signal characteristics that can be used to classify the actual spraying mode with a sample of measured current using both time and frequency domain analysis.
It is acquired the current data frame of 0.5s with 100 kHz as sampling frequency, with each current sample as 50 thousand current values. Through statistical analysis in these values such as mean, median and standard deviation the classification is done. 
Figure \ref{fig:sjaaks_statistical_class} illustrate data samples being classified using Sjaaks\cite{Sjaaks} method.

@@

To classify the multi jet, after running many steps experiments it was noticed that the multi jet signal has a similar shape as the cone jet but with a step in its current mean, also the cone jet current was almost fixed in all its voltage range. 
These effects were exposed by Ryan\cite{Ryan}. In his work he defines the relation between current per jet in both cone jet and multi jet modes.

With that, it was implemented the classification of the multi jet when the current mean is 1.14 above the expected cone jet current mean. 
The cone jet current can be calculated by the scaling laws \ref{sec:scalling-laws} formula.
The factor value of 1.14 was found by repeating a lot of experiments with the same liquid (pure ethanol), but varying the flow rate and the voltage. This factor value is just applied for pure ethanol, the liquid used in all experiments in this work.
The classification in the algorithm was divided in three steps as shown below.

@@

    The program developed is capable of running different types of routines and with an easy way to implement new strategies.
    Continuing the methodology, in the setup json file there is a "sequence" attribute which can be chosen between "ramp", "step", "map" or "control".
    The controller thread will manage what the algorithm must do for each sequence.
    Following the control model in Figure\ref{fig:control_model_fig}, the controller outputs (voltage and flow rate) are the actuators signal.
    The sampling rate is fixed to 0.5 seconds for all the experiments, and it's managed by the data\_acquisiton\_thread\ref{subsec:data_aquisition}.

@@

    In Figure \ref{fig:map2Data_fig} it can be seen the data acquired in this mapping experiments. The liquid used is pure ethanol. 
    Note that the experiment is composed of loops that increase voltage, change flow rate and repeat.

    \begin{figure}[H]
        \center
        \includegraphics[width=15cm]{Figuras/report2/map2Data.png}
        \caption{Mapping Experiment data collected. The Figure has 3 graphs with shared x-axis representing the samples collected. The first is the current values collected through all the experiment.
        The second is the voltage values applied in each window of data collected. The colors represent the spraying classification defined in the routine.
        The third graph shows the current mean value of each data sample.}
        \label{fig:map2Data_fig}
    \end{figure}

    With all the data collected, classified and saved in real time, further analysis and studies can be done. For example, Figure \ref{fig:map3Data_fig} illustrate the data automatically classified and displayed in a Voltage X Flow rate range of spraying modes with a specific liquid setup so that a comparison on automatic results with previous researches can be done, such as showed in Figure \ref{fig:ganan_calvo_fig}, validating the algorithm.

    \begin{figure}[H]
        \center
        \includegraphics[width=15cm]{Figuras/report4/map-2023-03-02.png}
        \caption{Mapping Experiment for pure ethanol in ambient conditions. The map shows the stability region of each electrospraying mode in the voltage and flow rate range.}
        \label{fig:map3Data_fig}
    \end{figure}

@@

    The control sequence is the only from the list of sequences that actually uses the feedback classification value. 
    As it is a closed loop control, the controller must be able to stabilize the system in the desired conditions.
    A simple controller algorithm is represented in algorithm \ref{alg:simple_controller}, and it was used as a proof of concept.
    Its results can be seen in results section \ref{sec:controller_results}.

@@

This chapter \ref{chap:Methodology} exhibits how the knowledge from chapter \ref{chap:lit_review} was implemented with a control and automation engineering approach in order to achieve the project goals. 
Next chapter \ref{chap:Results}, it will be discussed the results reached.
